%-------------------------
% Resume in LateX
% Author: Vladimir Ovechkin
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1,T2A]{fontenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english,russian]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Language selection mechanism
\newif\ifrussian

% Uncomment to use Russian
\russiantrue

% Bilingual text command - shows only one language based on the flag
\newcommand{\text}[2]{%
  \ifrussian#2\else#1\fi%
}

% Set the main document language
\ifrussian
  \selectlanguage{russian}
\else
  \selectlanguage{english}
\fi

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{mailto:me.vladimirovechkin@gmail.com}{\Large \text{Vladimir Ovechkin}{Владимир Овечкин}}} & \text{Email}{Эл. почта}: \href{mailto:me.vladimirovechkin@gmail.com}{me.vladimirovechkin@gmail.com}\\
  \href{https://www.linkedin.com/in/vladimir-ovechkin/}{linkedin.com/in/vladimir-ovechkin} & \text{Mobile}{Телефон}: \href{tel:+79956000615}{+7-995-600-06-15} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{
  \text
  {Education}
  {Образование}}

\resumeSubHeadingListStart
\resumeSubheading
{\text
  {ITMO University}
  {Университет ИТМО}}
{\text
  {St. Petersburg, Russia}
  {Санкт-Петербург, Россия}}
{\text
  {Bachelor in Computer Science; GPA: 4.50 / 5.00}
  {Бакалавр, Информационные системы и технологии; Оценка: 4.50 / 5.00}}
{\text
  {Sep 2017 -- Jun 2021}
  {Сен. 2017 -- Июн. 2021}}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section
 {\text
  {Experience}
  {Опыт работы}}

\resumeSubHeadingListStart
\resumeSubheading
{\text
  {Ecom.Tech}
  {Ecom.Tech}}
{\text
  {St. Petersburg, Russia}
  {Санкт-Петербург, Россия}}
{\text
  {Senior Software Engineer}
  {Старший разработчик}}
{\text
  {Aug 2022 -- Present}
  {Авг. 2022 -- Настоящее время}}
\resumeItemListStart
\resumeItem
{\text
  {Led the end-to-end launch process for 3 web products within the client support domain of more than 1000 unique users, overseeing all phases from inception to MVP release while consistently meeting aggressive deadlines.}
  {Руководил процессом запуска 3х веб-приложений в области клиентской поддержки с более чем 1000 пользователей, включая все этапы от концепции до выпуска MVP, стабильно соблюдая жесткие сроки.}}
\resumeItem
{\text
  {Provided supervision, leadership, and mentorship to a 3 new team members to achieve high performance and deliver MVP in time.}
  {Занимался наставничеством 3х новых членов команды для достижения высокой производительности и выпуска MVP в срок.}}
\resumeItem
{\text
  {Worked on Frontend stack set of JS technologies using Typescript, ES6/ESNext, ReactJS, GraphQL, Zustand, SASS, Jest, Webpack and Storybook in Agile/Scrum based project.}
  {Работал над фронтендом на JS стеке, используя Typescript, ES6/ESNext, ReactJS, GraphQL, Zustand, SASS, Jest, Webpack и Storybook в Agile/Scrum проекте.}}
\resumeItem
{\text
  {Developed and implemented a solution for integrating GraphQL with REST API of third-party services using Node.js, that allowed to reduce the number of tasks of the backend team by 30\%.}
  {Разработал и внедрил в компанию решение для интеграции GraphQL с REST API сторонних сервисов, на базе Node.js, что позволило сократить количество задач команды бекенда на 30\%.}}
\resumeItem
{\text
  {Developed and implemented a solution for rendering tables in the company using virtualization and an optimal way to load data from graphql, which improved performance and reduced page load time by up to 50\% for 3 applications.}
  {Разработал и внедрил в компанию решение для рендеринга таблиц, используя виртуализацию и оптимальный способ загрузки данных с graphql, что улучшило производительность и уменьшило время загрузки страниц до 50\% для 3х приложений.}}
\resumeItemListEnd

% --------Multiple Positions Heading------------
%  \resumeSubSubheading
%   {Software Engineer I}{Oct 2014 -- Sep 2016}
%   \resumeItemListStart
%      \resumeItem{Apache Beam}
%        {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%   \resumeItemListEnd

%-------------------------------------------

\resumeSubheading
{\text
  {Market Logic Software}
  {Market Logic Software}}
{\text
  {Sofia, Bulgaria}
  {София, Болгария}}
{\text
  {Software Engineer}
  {Разработчик}}
{\text
  {Jul 2021 -- Aug 2022}
  {Июль 2021 -- Авг. 2022}}
\resumeItemListStart
\resumeItem
{\text
  {Contributed to the development of 5 web platform micro-frontend modules utilizing TypeScript, React, and Redux within a collaborative team of 8 developers, serving a 100+ business customers worldwide.}
  {Внес вклад в разработку 5 микро-фронтендов веб-платформы, используя TypeScript, React и Redux в команде из 8 разработчиков, обслуживающих 100+ клиентов в бизнесе.}}
\resumeItem
{\text
  {Implemented comprehensive frontend code refactoring, resulting in a massive decrease in monthly new bug reports from 50 to 20 in average.}
  {Реализовал комплексный рефакторинг фронтенда, что привело к значительному сокращению ежемесячного количества новых багов с 50 до 20.}}
\resumeItem
{\text
  {Identified and resolved micro-frontend redundant dependencies issue, resulting up to 25\% speed-up in page load speed (TTI and bunch of other Lighthouse metrics) leads to increase in user engagement.}
  {Определил и устранил проблему лишних зависимостей в микро-фронтендах, что привело к росту скорости загрузки страницы до 25\% (TTI + метрики Lighthouse) и увеличению пользовательской вовлеченности.}}
\resumeItem
{\text
  {Implemented a frontend platform toolkit to optimize development processes, enhance code accuracy, and standardize the codebase, resulting in a significant reduction in development time and dev team satisfying rate.}
  {Реализовал инструмент для оптимизации процессов разработки и повышения стандартизации кода, что привело к значительному сокращению времени разработки и росту удовлетворенности разработчиков.}}
\resumeItemListEnd

\resumeSubheading
{\text
  {Bimdata}
  {Bimdata}}
{\text
  {St. Petersburg, Russia}
  {Санкт-Петербург, Россия}}
{\text
  {Fullstack Software Engineer}
  {Fullstack разработчик}}
{\text
  {May 2019 -- Jul 2021}
  {Май 2019 -- Июль 2021}}
\resumeItemListStart
\resumeItem
{\text
  {Development of a Software as a Service (SaaS) solution tailored for construction builders, achieving a valuation exceeding \$1 million.}
  {Разработка программного обеспечения в виде услуги (SaaS) для строительных компаний, достигшего оценки в 100 млн. рублей.}}
\resumeItem
{\text
  {Established Gitlab CI/CD pipelines for multiple products, ensuring efficient release management and publication processes, reducing time to production.}
  {Установил Gitlab CI/CD пайплайны для нескольких продуктов, что обеспечло эффективное управление релизами, сокращая время до выпуска на продакшен и количество багов.}}
\resumeItem
{\text
  {Implemented a comprehensive reusable component library, leading to a notable decrease in development time and reduced the number of bugs by 40\%.}
  {Реализовал комплексную библиотеку повторно переиспользуемых компонентов, что привело к значительному сокращению времени разработки и сократило количество багов до 40\%.}}
\resumeItem
{\text
  {Worked on a product's architecture to implement micro-frontend practices using Single-SPA to incorporate set of products into a unified cloud based application.}
  {Работал над архитектурой продукта для реализации микро-фронтенд подхода, используя Single-SPA для интеграции набора продуктов в единое облачное приложение.}}
\resumeItem
{\text
  {Provided task estimates, testing, reviews and production issue fixes, deployed projects to internal and production environments and achieved 95\% delivery of features that met SLAs in time.}
  {Обеспечивал оценку задач, тестирование, ревью кода и исправление багов. Занимался развертыванием проектов в тестовых и продовых окружениях, достигая 95\% доставки фич, соответствующих SLAs в срок.}}
\resumeItem
{\text
  {Integrated 3D model viewer to React application, used Three.js and Pixi.js to render 3D models.}
  {Интегрировал инструмент для просмотра 3D-моделей в React-приложение, используя Three.js и Pixi.js для рендеринга.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section
 {\text
  {Projects}
  {Проекты}}

\resumeSubHeadingListStart
\resumeSubItem
{\text
  {Eyelash Sofle keyboard}
  {Eyelash Sofle keyboard}}
{\text
  {Open source ergonomic keyboard with split design and customizable layout. Built with KiCad for pcb design and OpenScad for 3D printing case.}
  {Открытый исходный код эргономичной сплит клавиатуры с настраиваемой раскладкой. Разработан с использованием KiCad для дизайна печатных плат и OpenScad для 3D-печати корпуса.}}
\resumeSubItem
{\text
  {Pdfjs-custom-canvas}
  {Pdfjs-custom-canvas}}
{\text
  {Customized pdf.js library canvas wrapper for rendering pdf documents with custom styles and annotations.}
  {Кастомизированная обертка canvas библиотеки pdf.js для рендеринга pdf-документов с пользовательскими стилями и аннотациями.}}
\resumeSubHeadingListEnd

%--------SKILLS------------
\section
 {\text
  {Skills}
  {Навыки}}
\resumeSubHeadingListStart
\resumeSubItem
{\text
  {Languages}
  {Языки}}
{Python, JavaScript, TypeScript, SQL, Java}
\resumeSubItem
{\text
  {Technologies}
  {Технологии}}
{HTML, CSS/Sass, React, Redux, Next.js, Tailwind CSS, Node.js, Express, PostgreSQL, MongoDB, Git, Docker, Kubernetes}
\resumeSubHeadingListEnd

\end{document}
